\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amssymb, amsthm}
\usepackage{fullpage}
\usepackage{comment}
\usepackage{siunitx}

\usepackage[
    pdfusetitle,
    colorlinks
]{hyperref}

\title{Modeling and simulation of the SLM process}
\date{\today}
\author{Oleg Rogozin}

% general
\newcommand{\dder}[2][]{\Delta_{#2}#1}
\newcommand{\pder}[2][]{\frac{\partial#1}{\partial#2}}
\newcommand{\pderdual}[2][]{\frac{\partial^2#1}{\partial#2^2}}
\newcommand{\pderder}[3][]{\frac{\partial^2#1}{\partial#2\partial#3}}
\newcommand{\Pder}[2][]{\partial#1/\partial#2}
\newcommand{\Pderdual}[2][]{\partial^2#1/\partial#2^2}
\newcommand{\Pderder}[3][]{\partial^2#1/\partial#2\partial#3}
\DeclarePairedDelimiter\autobracket()       % mathtools are needed
\newcommand{\br}[1]{\autobracket*{#1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\OO}[1]{O(#1)}
\newcommand{\pert}[1]{\delta#1}
\newcommand{\diag}[1]{\left(#1\right)^\mathrm{diag}}

% topic-specific
\newcommand{\fusion}[1]{{#1}^\mathrm{fus}}

\begin{document}
\maketitle
\tableofcontents

\section{Formulation of the problem}

%%% The first law of thermodynamics
The conservation of energy for a substance at rest is described by the \(D\)-dimensional heat-conduction equation
\begin{equation}\label{eq:heat_conduction}
	\rho\pder[h(T)]{t} = \pder{x_i}\br{ k(\psi,T)\pder[T]{x_i} },
\end{equation}
where \(x_i\) are the physical coordinates (\si{m}), \(t\) is the time (\si{s}),
\(\rho\) is the density (\si{kg/m}\(^D\)), \(h\) is the specific enthalpy (\si{J/kg}),
\(T\) is the temperature (\si{\K}), \(k\) is the thermal conductivity (\si{W/Km}\(^{D-2}\)),
\(\psi\) is the porosity. Let
\begin{equation}\label{eq:porosity_variables}
	\rho = \rho_0(1-\psi_0), \quad k = k_0(T)(1-\psi),
\end{equation}
where \(\rho_0\) and \(k_0\) is the density and thermal conductivity of the bulk material, respectively,
\(\psi_0\) is the initial porosity.

%%% Introduce a liquid fraction
To incorporate the fusion process into the model, let the enthalpy depends on the temperature as follows:
\begin{equation}\label{eq:enthalpy}
	h = \int_{T_0}^T c_p(\xi)\dd\xi + \fusion{h}\phi(h),
\end{equation}
where \(c_p\) is the specific heat capacity (\si{J/kgK}), \(\fusion{h}\) is the specific enthalpy of fusion (\si{J/kg}),
\(\phi\) is the liquid fraction (\(0 \leq \phi \leq 1\)), which is monotonic function of \(h\).
Assume that
\begin{equation}\label{eq:liquid_fraction}
	\phi(h<h_S) = \OO{\br{h_S-h}^{-\infty}}, \quad \phi(h>h_L) = \OO{\br{h-h_L}^{-\infty}},
\end{equation}
where \(h_S = h(T_S)\) and \(h_L = h(T_L)\).
\(T_S\) and \(T_L\) are the solidus and liquidus temperatures, respectively.
Substituting~\eqref{eq:porosity_variables} and~\eqref{eq:enthalpy} into~\eqref{eq:heat_conduction}, we obtain
\begin{equation}\label{eq:heat_conduction2}
	\rho_0\pder[h]{t} = \pder{x_i}\br{ \frac{1-\psi}{1-\psi_0} \frac{k_0(T)}{c_p(T)}\pder[h_*]{x_i} },
\end{equation}
where \(h_* = h - \fusion{h}\phi\) is introduced for convenience.

%%% Change in thermophysical properties resulting from fusion process
The phase transition results in an abrupt change in the thermophysical properties \(f=c_p,k_0\) of the material;
therefore, they can be expressed as
\begin{equation}\label{eq:fusion_change}
	f = f_S(T) + \br{ f_L(T) - f_S(T)}\phi,
\end{equation}
where \(f_S\) and \(f_L\) correspond to solid and liquid properties.
The porosity change is irreversible in time:
\begin{equation}\label{eq:porosity}
	\psi(t) = \psi_0\min_{0\leq\tau\leq t}\br{ 1-\phi(h(\tau)) }.
\end{equation}

%%% Initial and boundary conditions
Consider a half-space problem \(x_D<0\) with the following boundary condition at \(x_D=0\):
\begin{equation}\label{eq:bc}
	k(\psi,T)\pder[T]{x_D} = \frac{A(\psi)P}{(\pi R^2)^{(D-1)/2}}\exp\br{ -\frac{(x_i-x_{Bi}(t))^2}{R^2} }
	    - \alpha(T-T_0) - \epsilon\sigma T^{D+1},
\end{equation}
where \(A\) is the absorptivity, \(P\) is the laser power (\si{W}), \(R\) is the radius of the laser beam (\si{m}),
\(x_{Bi}\) are the coordinates of its center (\si{m}), \(\alpha\) is the convective heat transfer coefficient (\si{W/Km}\(^{D-1}\)),
\(\epsilon\) is the emissivity, \(\sigma\) is the Stefan--Boltzmann constant (\si{W/K}\(^{D+1}\)\si{m}\(^{D-1}\)).
The initial condition is \(T=T_0\) at \(t=0\).

\subsection{Dimensionless expressions}

Introduce the following dimensionless variables:
\begin{equation}\label{eq:dimensionless}
    \begin{aligned}
        x_i &= \hat{x}_iR, & t &= \hat{t}t_0, & h &= \hat{h}c_p(T_0)\Delta{T}, & T - T_0 &= \hat{T}\Delta{T}, \\
        P &= \hat{P} k_0(T_0)\Delta{T}R^{D-2}, & \alpha &= \hat{\alpha}\frac{k_0(T_0)}R, &
            \sigma &= \hat{\sigma}\frac{k_0(T_0)}{R\Delta{T}^3}, & T_0 &= \hat{T}_0\Delta{T}, \\
    \end{aligned}
\end{equation}
where \(t_0 = \rho_0 c_p(T_0) R^2/k_0(T_0)\) is the diffusive time scale at \(T=T_0\),
\(\Delta{T} = (T_S+T_L)/2 - T_0\) is the unit temperature.
If \(|\Pder[x_{Bi}]{t}|\) is of order \(U_0\), where \(U_0\) is the reference scanning speed (\si{m/s}),
then \(R/U_0\) is the convective time scale. Also denote
\begin{equation}
    \hat{c}_p(\hat{T}) = \frac{c_p(T)}{c_p(T_0)}, \quad
    \hat{k}_0(\hat{T}) = \frac{k_0(T)}{k_0(T_0)}, \quad
    \hat{\phi}(\hat{h}) = \phi(h), \quad
    \hat{\psi}(\hat{h}) = \psi(h).
\end{equation}
Then~\eqref{eq:enthalpy},~\eqref{eq:heat_conduction2}, and~\eqref{eq:bc} take the following nondimensional form:
\begin{gather}
	\hat{h}_* \equiv \hat{h} - \fusion{\hat{h}}\hat{\phi} = \int_0^{\hat{T}} \hat{c}_p(\xi)\dd\xi, \label{eq:enthalpy_hats} \\
	\pder[\hat{h}]{\hat{t}} = \pder{\hat{x}_i}\br{
	    \frac{1-\hat{\psi}}{1-\psi_0}
	    \frac{\hat{k}_0(\hat{T})}{\hat{c}_p(\hat{T})}\pder[\hat{h}_*]{\hat{x}_i}
	}, \label{eq:heat_conduction_hats} \\
	\br{1 - \hat{\psi}} \frac{\hat{k}_0(\hat{T})}{\hat{c}_p(\hat{T})}\pder[\hat{h}_*]{\hat{x}_D} +
	    \hat{\alpha}\hat{T} + \epsilon\hat{\sigma} \br{ \hat{T} + \hat{T}_0 }^4 =
	    \frac{A(\psi)\hat{P}}{\pi^{(D-1)/2}}\exp\br{ -\br{ \hat{x}_i-\hat{x}_{Bi}(t) }^2 }. \label{eq:bc_hats}
\end{gather}
The initial condition is \(\hat{h} = 0\).

\section{Liquid fraction models}

\subsection{Piecewise approximation}

Let the dependence on temperature be linear, i.e.,
\begin{gather}
	\hat{f} = 1 + \hat{f}'_S\hat{T} + \left[
	    \fusion{\hat{f}} + \br{ \hat{f}'_L - \hat{f}'_S }\br{ \hat{T}-1 }
	\right], \\
	\hat{\phi} = \begin{cases}
        0 & \quad \hat{h} \leq \hat{h}_S, \\
        \frac{\hat{h}-\hat{h}_S}{\hat{h}_L-\hat{h}_S} & \quad \hat{h}_S < \hat{h} < \hat{h}_L, \\
        1 & \quad \hat{h}_L \leq \hat{h},
    \end{cases}
\end{gather}
where \(\fusion{\hat{f}}\) is the property jump at the phase transition.

If \(\hat{c}'_{pL} = \hat{c}'_{pS} = \hat{c}'_p\) and \(\fusion{\hat{c}_{p}} = 0\),
then~\eqref{eq:enthalpy_hats} can be rewritten as
\begin{equation}\label{eq:temperature}
	\hat{T} = \frac{\sqrt{1+2\hat{c}_p'\hat{h}_*}-1}{\hat{c}_p'},
\end{equation}
when \(\hat{c}_p'>0\) and \(\hat{T} = \hat{h}_*\) when \(\hat{c}_p'=0\).

\section{Numerical methods}

For~\eqref{eq:heat_conduction_hats}, we can write
\begin{gather}
    F = \dder{\hat{x}_i}\br{
        \frac{1 - \hat{\psi}}{1 - \psi_0}
	    \frac{1 + \hat{k}'\hat{T}}{1 + 2\hat{c}_p'\hat{T}}
	    \dder[\hat{h}_*]{\hat{x}_i}
	}, \\
    \pert{F} = \dder{\hat{x}_i}\left[ \frac{1 - \hat{\psi}}{1 - \psi_0} \br{
	    \frac{(\hat{k}' - 2\hat{c}_p')\pert{\hat{h}_*}}{(1 + 2\hat{c}_p'\hat{T})^3}
	     \dder[\hat{h}_*]{\hat{x}_i}
	    +
	    \frac{1 + \hat{k}'\hat{T}}{1 + 2\hat{c}_p'\hat{T}}
	    \dder[\pert{\hat{h}_*}]{\hat{x}_i}
	}\right], \\
    \diag{\pert{F}} \approx \frac{1 - \hat{\psi}}{1 - \psi_0} \br{
	    \frac{\hat{k}' - 2\hat{c}_p'}{(1 + 2\hat{c}_p'\hat{T})^3} \dder[\hat{h}_*]{\hat{x}_i} \diag{\dder{\hat{x}_i}}
	    +
	    \frac{1 + \hat{k}'\hat{T}}{1 + 2\hat{c}_p'\hat{T}}
	    \diag{\dder{\hat{x}_i}^2}
	}\diag{\pert{\hat{h}_*}}.
\end{gather}
where
\begin{gather}
    \pert{\hat{h}_*} = \pert{\hat{h}} - \fusion{\hat{h}}\pert{\hat\phi}, \quad
    \diag{\hat{h}_*} = \diag{\pert{\hat{h}_*}} = 1 - \fusion{\hat{h}}\diag{\pert{\hat\phi}}, \\
	\pert{\hat{\phi}} = \begin{cases}
        0 & \quad \hat{h} \leq \hat{h}_S, \quad \hat{h}_L \leq \hat{h}, \\
        \pert{\hat{h}}/(\hat{h}_L-\hat{h}_S) & \quad \hat{h}_S < \hat{h} < \hat{h}_L, \\
    \end{cases} \label{eq:pert_phi_h}\\
	\diag{\pert{\hat{\phi}}} = \begin{cases}
        0 & \quad \hat{h} \leq \hat{h}_S, \quad \hat{h}_L \leq \hat{h}, \\
        1/(\hat{h}_L-\hat{h}_S) & \quad \hat{h}_S < \hat{h} < \hat{h}_L. \\
    \end{cases} \label{eq:pert_phi_h_diag}
\end{gather}

Nonlinear dependence~\eqref{eq:temperature} can be linearized; therefore, we have the following linear boundary condition at \(z=0\):
\begin{equation}\label{eq:bc_linearized}
	\br{ \hat{\alpha} + \frac{1 - \hat{\psi}^n}{1 - \psi_0}\br{ 1 + \hat{k}'\hat{T}^n }\pder{\hat{x}_3} }
	    \br{ \hat{T}^n + \frac{\hat{h}_* - \hat{h}_*^n}{1+2\hat{c}_p'\hat{T}^n} }
	    = \frac{A\hat{P}}{\pi}\exp\br{ -(\hat{x}_1-\hat{U}\hat{t}^n)^2 - \hat{x}_2^2 },
\end{equation}
where superscripts \(n\) and \(n+1\) correspond to the previous and current iterations, respectively.

\end{document}

0 = T + c'T^2 + phi - h
T = (-1+\sqrt{1+4c'(h-phi)})/2c'
\psi = \psi_0 -- \phi=0
\psi = 0      -- \phi=1
\psi = \psi_0 - \phi\psi_0

